Solar wind, F10.7, and geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit

### 2016-08-18 paper/paper.tex
Misc edit

% Hourly averages are required to show a statistically significant mass density response during high geomagnetic activity
% The response of mass density for high geomagnetic activity intervals is strongest when F10.7 is elevated
% There is no solar wind variation signature associated with large mass density events

\begin{abstract}
We consider two types of events, identified by decreases in $D_{st}$ below a threshold value and increases in the the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value using the \cite{Takahashi2010} dataset.  From the $D_{st}$ events and 1-day averages, we find that there is a statistically weak and small-amplitude difference between $\rho_{eq}$ on the day of the event and the days before and after.  When hourly averages are considered, a signficant peak is found to occur six hours after event onset and the primary factor that determines the post-onset peak amplitude in $\rho_{eq}$ in the hourly averages is elevated $F10.7$.  In addition, for hourly averages, $\rho_{eq}$ following the onset of a $D_{st}$ event does not depend on the north-south component of the interplanetary magnetic field, $B_z$ near the time of onset.  From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ four hours after the event onset corresponding to larger $\rho_{eq}$ values 24-36 hours after onset.  In contrast, the average of $B_z$ four hours prior to $\rho_{eq}$ events does not have a statistically significant impact on $\rho_{eq}$ after onset.
\end{abstract}
%\vspace{2em}
%\hrule
%\vspace{2em}
% \end{@twocolumnfalse}
%  ]

>>>>

% Key points
% Hourly averages are required to show a statistically significant mass density response during high geomagnetic activity
% The response of mass density for high geomagnetic activity intervals is strongest when F10.7 is elevated
% There is no solar wind variation signature associated with large mass density events

% Reviewers
% Takahashi
% O'Brien
% Denton
% Galager
% Singer

\begin{abstract}
We consider two types of events, identified by decreases in $D_{st}$ below a threshold value and increases in the the equatorial mass density at geosynchronous altitudes, $\rho_{eq}$, above a threshold value using the \cite{Takahashi2010} dataset.  From the $D_{st}$ events and 1-day averages, we find that there is a statistically weak and small-amplitude difference between $\rho_{eq}$ on the day of the event and the days before and after.  When hourly averages are considered, a signficant peak is found to occur six hours after event onset, and the primary factor that determines the post-onset peak amplitude in $\rho_{eq}$ is elevated $F10.7$.  In addition, for hourly averages, $\rho_{eq}$ following the onset of a $D_{st}$ event does not depend on the north-south component of the interplanetary magnetic field, $B_z$ near the time of onset.  From the $\rho_{eq}$ events, we find a weak dependence on $B_{z}$ after the onset of an event, with higher average $B_{z}$ four hours after the event onset corresponding to larger $\rho_{eq}$ values 24-36 hours after onset.  In contrast, the average of $B_z$ four hours prior to $\rho_{eq}$ events does not have a statistically significant impact on $\rho_{eq}$ after onset.
\end{abstract}
%\vspace{2em}
%\hrule
%\vspace{2em}
% \end{@twocolumnfalse}
%  ]
